A thesis draft

### 2018-10-03 draft.tex
Start talking about VIBES architecture

>>>>

\subsection{VIBES architectural description}

In the original VIBES architectural design, based on leveraging virtualization 
technologies, is possible to identify different macro-components, each of these 
specialized in fullfilling a specific goal. For the ETSI standards, the Network 
Function Virtualization (NFV) design should be composed as follows:\todo{Insert 
image page 11 ETSI vibes specification}
\begin{itemize}
 \item Network Function Virtualization Infrastructure (NFVI): it's the heart of 
the whole computation component, and here three sub-domains can be identified:
\todo{Expand this section}
\begin{itemize} 
 \item Hypervisor domain that is composed of the Virtual Compute, the Virtual 
Storage, and the Virtualization Layer. These components
 \item Compute domain composed by the Physical Compute and the Physical Storage
 \item Infrastructure domain which has the Physical Network, and its 
virtualized counterpart as made available by the Virtualization Layer
\end{itemize}

\end{itemize}
